---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

indices of matched individuals 
```{r}
ind_Treat <- c(1, 4, 13, 15, 16, 18, 20, 21, 23, 26)
ind_Kont <- c(10, 16, 23, 31, 35, 37, 38, 41, 42, 47, 48, 49, 50, 51, 52, 60,
              61, 65, 68, 81, 83, 91, 95, 96, 97)
```
source function to process raw eye tracking data
```{r}
source('R/Transform_data.R')
```

### Stimulus car cornfield

```{r}
EyePos_example_M_v18 <- Transform_data(path = 'Data_vid18/Vid18_car_cornfield_treatments.csv')
str(EyePos_example_M_v18)
EyePos_example_M_v18_Matched <- EyePos_example_M_v18[, , ind_Treat]
str(EyePos_example_M_v18_Matched)
```

```{r}
EyePos_example_K_v18 <- Transform_data(path = 'Data_vid18/Vid18_car_cornfield_controls.csv')
str(EyePos_example_K_v18)
EyePos_example_K_v18_Matched <- EyePos_example_K_v18[, , ind_Kont]
str(EyePos_example_K_v18_Matched)
```

## group comparison 

load multi-group model
```{r}
source('R/modeling_multigroup.R')
```
load AoIs
```{r }
load('Data_vid18/car.corn_dynamic_AOI.Rdata') 
load('Data_vid18/car.corn_static_AOI.Rdata') 
```
model for the first 70 frames (the runtime is quite long)
```{r cache = TRUE}
Lasso_Group_vid18 <- 
  Final_Lasso(EyePos_example_Treat = EyePos_example_M_v18_Matched, 
            EyePos_example_Cont = EyePos_example_K_v18_Matched,
            vidheight = 576, vidwidth = 720,
            vidheight_monitor = 1080, vidwidth_monitor = 1350, Nmap = 6, 
            nframes = 70, path_all = "./Data_vid18",
            listname_AOI_dyn = List_AOI_car.cornfield_dyn, 
            listname_AOI_stat = AOI_car.cornfield_stat, least_squares = TRUE,
            lasso = TRUE, Permutation = FALSE)
```



Graphical illustration of the coefficients of determination $R^2$
```{r }
plot(Lasso_Group_vid18$r2_adj)
```
Graphical illustration of the feature map weights
```{r eval=F}
beta <- Lasso_Group_vid18$betakq
beta[is.na(beta)] <- 0

beta_norm <- matrix(nrow = nrow(beta), ncol = ncol(beta))
beta_norm[, 1] <- beta[, 1] 
beta_norm[, 2] <- beta[, 2]
beta_norm[, 3] <- beta[, 3]
beta_norm[, 4] <- beta[, 4]
beta_norm[, 5] <- beta[, 5]
beta_norm[, 6] <- beta[, 6]

beta_norm[, 7] <- beta[, 7] + beta[, 1]
beta_norm[, 8] <- beta[, 8] + beta[, 2]
beta_norm[, 9] <- beta[, 9] + beta[, 3]
beta_norm[, 10] <- beta[, 10] + beta[, 4]
beta_norm[, 11] <- beta[, 11] + beta[, 5]
beta_norm[, 12] <- beta[, 12] + beta[, 6]

require('plotly')

plot_ly(x = ~1:nrow(beta_norm), y = ~beta_norm[, 1], name = 'Static', 
        mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 1], name = 'Static Control', color = I("blue"),
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 2], name = 'Dynamic Control', color = I("orange"), 
            mode = 'lines'
            ) %>%
  add_trace(y = ~beta_norm[, 3], name = 'Center Bias Control', 
            color = I("darkgreen"),
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 4], name = 'Uniform Control', color = I("red"), 
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 5], name = 'AOI1 Control', color = I("purple"),
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 6], name = 'AOI2 Control', color = I("brown"), 
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 7], name = 'Static Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("blue"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 8], name = 'Dynamic Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("orange"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 9], name = 'Center Bias Treat',
            line = list(widthh=0.5, dash="dot"),
            color = I("darkgreen"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 10], name = 'Uniform Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("red"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 11], name = 'AOI1 Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("purple"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 12], name = 'AOI2 Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("brown"), mode = 'lines') %>%
  layout(
   # title = "Relative importance curves (car.cornfield, Frame 2-70)",
      xaxis = list(title = "Frame number"),
      yaxis = list(title = "Feature map weight")
    ) %>%
  layout(legend = list(orientation = 'h'))
```
LASSO vs. KQ


$Y_j  =  \beta_U  {M}_{Uj} + \beta_{CB}  M_{CBj} + \beta_{S}  M_{Sj} + \beta_D M_{Dj} + \beta_{AOI1}M_{AOI1j} + \beta_{AOI2} M_{AOI2j} +   \beta_{U,G}  (M_{Uj} \cdot M_{Gj}) + \beta_{CB,G} (M_{CBj}\cdot M_{Gj}) + \beta_{S,G}  (M_{Sj}  \cdot M_{Gj}) +$
$\beta_{D,G} (M_{Dj} \cdot M_{Gj}) +\beta_{AOI1,G} (M_{AOI1j} \cdot M_{Gj}) +  \beta_{AOI2,G} (M_{AOI2j} \cdot M_{Gj}) + \epsilon_j$
```{r}
Names <- c("Static", "Dynamic", "CB", "Unif", "AOI Dyn", "AOI Stat",
           "Static Group", "Dynamic Group", "CB Group", "Unif Group", 
           "AOI Dyn Group", "AOI Stat Group")
beta_kq <- Lasso_Group_vid18$betakq
beta <- Lasso_Group_vid18$beta
{par(mfrow = c(2, 2))
for(i in 1:ncol(beta)){
  
  plot(beta[,i], type = "l", col = "blue", main = Names[i])
  points(beta_kq[,i], type = "l", col = "green")
  if(i == 1){
  legend("topleft", legend = c("lasso", "ls"), lwd = 1, col = c("blue", "green"))}
}
}
```

Permutation test

```{r}
# random assignment of persons to groups of size 10 (treatment) and 25 (control)
library(abind)
# combine data:
EyePos_komb <- abind(EyePos_example_M_v18_Matched, EyePos_example_K_v18_Matched, 
                     along = 3)
str(EyePos_komb)
```

```{r}
set.seed(123)
Permutation_vid18 <- list()
for(i in 1:1000){
  index_Treat <- sample(1:dim(EyePos_komb)[3], 
                        size = dim(EyePos_example_M_v18_Matched)[3])
  
  Random_Treat <- EyePos_komb[,,index_Treat]
  Random_Cont <- EyePos_komb[,,-index_Treat]
  
  
  
  
  
   fit.ls <- Final_Lasso(EyePos_example_Treat = Random_Treat, 
                                         EyePos_example_Cont = Random_Cont,
                                         vidheight = 576, 
                                         vidwidth = 720,
                                         vidheight_monitor = 1080, 
                                         vidwidth_monitor = 1350, 
                                         Nmap = 6, 
                                         nframes = 70, 
                                         path_all = "./Data_vid18",
                                         listname_AOI_dyn = List_AOI_car.cornfield_dyn, 
                                         listname_AOI_stat = AOI_car.cornfield_stat,
                                         least_square = TRUE,
                                         lasso = FALSE, 
                                         Permutation = TRUE)
   
   Permutation_vid18[[i]] <- fit.ls
}
```

```{r}
nframes=70

chosen_frames <- round(seq(7, nframes, len = 10))
beta_observed <- Lasso_Group_vid18$betakq[chosen_frames, 7:12]



str(Permutation_vid18)
featmap <- c("Static", "Dynamic", "CB", "Uniform", "AoI1", "AoI2")

beta.df <- matrix(nrow = 1000 * 6 * 10, ncol = 5)
colnames(beta.df) <- c("Frame", "Replication", "Featuremap", "beta_estimated", 
                       "beta_observed")

row <- 0

for(frame in 1:10){

  for(i in 1:1000){
    
    for(fm in 7:12){
      row <- row + 1
      beta.df[row, ] <- c(paste("Frame", chosen_frames[frame]), 
                          i, featmap[fm - 6], 
                          Permutation_vid18[[i]]$betakq[frame, fm],
                          beta_observed[frame, fm - 6])
    }
  }
  
}

beta.df <- as.data.frame(beta.df)

beta.df$Featuremap <- as.character(factor(beta.df$Featuremap, level = unique(beta.df$Featuremap)))

p <- ggplot(data = beta.df, aes(x = Featuremap, y = as.numeric(beta_estimated), 
                                fill = Featuremap)) + 
             geom_boxplot(aes(fill=Featuremap)) + 
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
  geom_point(mapping = aes(x = Featuremap, y = as.numeric(beta_observed)),
            color = 'red', pch = 3)

p + facet_wrap( ~ factor(Frame, levels = unique(beta.df$Frame)), #scales = "free", 
                ncol = 5, nrow = 2)  +
  xlab("Feature Map") + ylab("Estimated group difference coefficient") + guides(fill=guide_legend(title = "Feature Map"))





boxplot(beta.df[Frame == frame])
```





### Stimulus walking market



```{r}
EyePos_example_M_v26 <- Transform_data(path = 'Data_vid26/Vid26_walking_market_treatment.csv')
str(EyePos_example_M_v26)
EyePos_example_M_v26_Matched <- EyePos_example_M_v26[, , ind_Treat]
str(EyePos_example_M_v26_Matched)
```

```{r}
EyePos_example_K_v26 <- Transform_data(path = 'Data_vid26/Vid26_walking_market_control.csv')
str(EyePos_example_K_v26)
EyePos_example_K_v26_Matched <- EyePos_example_K_v26[, , ind_Kont]
str(EyePos_example_K_v26_Matched)
```

## group comparison 

load AoIs
```{r }
load('Data_vid26/walking.market_dynamic_AOI.Rdata') 
load('Data_vid26/walking.market_static_AOI.Rdata') 
```
model for the first 70 frames (the runtime is quite long)
```{r cache = TRUE}
Lasso_Group_vid26 <- 
  Final_Lasso(EyePos_example_Treat = EyePos_example_M_v26_Matched, 
            EyePos_example_Cont = EyePos_example_K_v26_Matched,
            vidheight = 576, vidwidth = 720,
            vidheight_monitor = 1080, vidwidth_monitor = 1350, Nmap = 6, 
            nframes = 70, path_all = "./Data_vid26",
            listname_AOI_dyn = List_AOI_walking.market_dyn, 
            listname_AOI_stat = AOI_walking.market_stat, 
            least_squares = TRUE,
            lasso = FALSE, Permutation = FALSE)
```

Graphical illustration of the feature map weights
```{r eval=F}
beta <- Lasso_Group_vid26$betakq
beta[is.na(beta)] <- 0

beta_norm <- matrix(nrow = nrow(beta), ncol = ncol(beta))
beta_norm[, 1] <- beta[, 1] 
beta_norm[, 2] <- beta[, 2]
beta_norm[, 3] <- beta[, 3]
beta_norm[, 4] <- beta[, 4]
beta_norm[, 5] <- beta[, 5]
beta_norm[, 6] <- beta[, 6]

beta_norm[, 7] <- beta[, 7] + beta[, 1]
beta_norm[, 8] <- beta[, 8] + beta[, 2]
beta_norm[, 9] <- beta[, 9] + beta[, 3]
beta_norm[, 10] <- beta[, 10] + beta[, 4]
beta_norm[, 11] <- beta[, 11] + beta[, 5]
beta_norm[, 12] <- beta[, 12] + beta[, 6]

require('plotly')

plot_ly(x = ~1:nrow(beta_norm), y = ~beta_norm[, 1], name = 'Static', 
        mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 1], name = 'Static Control', color = I("blue"),
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 2], name = 'Dynamic Control', color = I("orange"), 
            mode = 'lines'
            ) %>%
  add_trace(y = ~beta_norm[, 3], name = 'Center Bias Control', 
            color = I("darkgreen"),
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 4], name = 'Uniform Control', color = I("red"), 
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 5], name = 'AOI1 Control', color = I("purple"),
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 6], name = 'AOI2 Control', color = I("brown"), 
            mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 7], name = 'Static Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("blue"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 8], name = 'Dynamic Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("orange"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 9], name = 'Center Bias Treat',
            line = list(widthh=0.5, dash="dot"),
            color = I("darkgreen"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 10], name = 'Uniform Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("red"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 11], name = 'AOI1 Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("purple"), mode = 'lines') %>%
  add_trace(y = ~beta_norm[, 12], name = 'AOI2 Treat', 
            line = list(widthh=0.5, dash="dot"),
            color = I("brown"), mode = 'lines') %>%
  layout(
   # title = "Relative importance curves (car.cornfield, Frame 2-70)",
      xaxis = list(title = "Frame number"),
      yaxis = list(title = "Feature map weight")
    ) %>%
  layout(legend = list(orientation = 'h'))
```




Permutation test

```{r}
# random assignment of persons to groups of size 10 (treatment) and 25 (control)
library(abind)
# combine data:
EyePos_komb <- abind(EyePos_example_M_v26_Matched, EyePos_example_K_v26_Matched, 
                     along = 3)
str(EyePos_komb)
```

```{r eval=FALSE}
set.seed(123)
Permutation_vid26 <- list()
for(i in 1:1000){
  index_Treat <- sample(1:dim(EyePos_komb)[3], 
                        size = dim(EyePos_example_M_v26_Matched)[3])
  
  Random_Treat <- EyePos_komb[,,index_Treat]
  Random_Cont <- EyePos_komb[,,-index_Treat]
  
  
  
  
  
   fit.ls <- Final_Lasso(EyePos_example_Treat = Random_Treat, 
                                         EyePos_example_Cont = Random_Cont,
                                         vidheight = 576, 
                                         vidwidth = 720,
                                         vidheight_monitor = 1080, 
                                         vidwidth_monitor = 1350, 
                                         Nmap = 6, 
                                         nframes = 70, 
                                         path_all = "./Data_vid26",
                                         listname_AOI_dyn = List_AOI_walking.market_dyn, 
                                         listname_AOI_stat = AOI_walking.market_stat,
                                         least_squares = TRUE,
                                         lasso = FALSE, 
                                         Permutation = TRUE)
   
   Permutation_vid26[[i]] <- fit.ls
}
```

```{r}
nframes=70

chosen_frames <- round(seq(7, nframes, len = 10))
beta_observed <- Lasso_Group_vid26$betakq[chosen_frames, 7:12]



str(Permutation_vid26)
featmap <- c("Static", "Dynamic", "CB", "Uniform", "AoI1", "AoI2")

beta.df <- matrix(nrow = 1000 * 6 * 10, ncol = 5)
colnames(beta.df) <- c("Frame", "Replication", "Featuremap", "beta_estimated", 
                       "beta_observed")

row <- 0

for(frame in 1:10){

  for(i in 1:1000){
    
    for(fm in 7:12){
      row <- row + 1
      beta.df[row, ] <- c(paste("Frame", chosen_frames[frame]), 
                          i, featmap[fm - 6], 
                          Permutation_vid26[[i]]$betakq[frame, fm],
                          beta_observed[frame, fm - 6])
    }
  }
  
}

beta.df <- as.data.frame(beta.df)

beta.df$Featuremap <- as.character(factor(beta.df$Featuremap, level = unique(beta.df$Featuremap)))

p <- ggplot(data = beta.df, aes(x = Featuremap, y = as.numeric(beta_estimated), 
                                fill = Featuremap)) + 
             geom_boxplot(aes(fill=Featuremap)) + 
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
  geom_point(mapping = aes(x = Featuremap, y = as.numeric(beta_observed)),
            color = 'red', pch = 3)

p + facet_wrap( ~ factor(Frame, levels = unique(beta.df$Frame)), #scales = "free", 
                ncol = 5, nrow = 2)  +
  xlab("Feature Map") + ylab("Estimated group difference coefficient") + guides(fill=guide_legend(title = "Feature Map"))

```
